\textbf{Varying coefficients correlated velocity models in complex landscapes with application to narwhal behavioral response to ship exposure and airgun exposure}

### 2024-04-28 Latex/main.tex
reorganization of the paper

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.4]{images/simulation study/illustrative_sample_rect.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.4]{images/simulation study/illustrative_sample_fjords.png}
		\caption{}
	\end{subfigure}
	\caption{Samples of the CRCVM in different domains. x and y axis are in metres and initial positions are indicated by a red cross and red point represent the nearest points on the boundary of the domain (a) One sample three day sample with time step $h=1$ min in a rectangular domain (b) One sample three day sample with time step $h=1$ min in Scoresby Sound fjords system in South-East Greenland}
	\label{fig: samples_rect_CRCVM}
\end{figure}

@@

\subsection{Estimation with tensor splines}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.3]{images/simulation study/omega_crcvm_fjords_hf_ne1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.3]{images/simulation study/omega_crcvm_fjords_hf_ne1.png}
		\caption{}
	\end{subfigure}
	\caption{Estimates of the smooth parameter $\omega$ as a function of $D_{shore}$ and $\Theta$ in Scoresby Sound fjords system. (a)-(b): Estimation from data with time step $h=1$ min (high frequency) with respective measurement errors standard deviation $\sigma_{obs}=3$ m and $\sigma_{obs}=30$ m.}
	\label{fig: estimate_fjords_CRCVM}
\end{figure}

@@

@@

		\log(\tau^{(i)}_j)=\log(\tau_{pre})+b_{\tau,pre}^{(i)} \\
		\log(\nu^{(i)}_j)=\log(\nu_{pre})+b_{\nu,pre}^{(i)}  \\
		\omega^{(i)}_j=\omega_{0,pre}+\sum_{k=1}^{L} \omega_{k,pre} \psi_k(E_{shore}^{(i)}(t_j^{(i)}),\Theta^{(i)}(t_j^{(i)})) + b_{\omega,pre}^{(i)}
	\end{array}
	\right.
	\label{eq: approximate baseline model}
\end{equation}

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.3]{images/simulation study/illustrative_sample_rect.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.3]{images/simulation study/illustrative_sample_fjords.png}
		\caption{}
	\end{subfigure}
	\caption{Samples of the CRCVM in different domains. x and y axis are in metres and initial positions are indicated by a red cross and red point represent the nearest points on the boundary of the domain (a) One sample three day sample with time step $h=1$ min in a rectangular domain (b) One sample three day sample with time step $h=1$ min in Scoresby Sound fjords system in South-East Greenland}
	\label{fig: samples_rect_CRCVM}
\end{figure}

@@

\subsection{Estimation of angular velocity $\omega$ with tensor splines}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.3]{}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[scale=0.3]{}
		\caption{}
	\end{subfigure}
	\caption{Estimates of the smooth parameter $\omega$ as a function of $D_{shore}$ and $\Theta$ in Scoresby Sound fjords system. (a)-(b): Estimation from data with time step $h=1$ min (high frequency) with respective measurement errors standard deviation $\sigma_{obs}=3$ m and $\sigma_{obs}=30$ m.}
	\label{fig: estimate_fjords_CRCVM}
\end{figure}

@@

\begin{equation}  \left\{
	\begin{array}{l}
		Y_{ij}=X_{ij}+\varepsilon_{ij} \quad j \in \{1,\cdots,n_{i,pre}\}\\
		\varepsilon_{ij} \underset{i.i.d}{\sim} \mathcal{N}(0,\sigma_{obs}^2)  \\
		dX_i(t)=V_i(t)dt  \\
		dV_i(t)=-\begin{pmatrix} 
			\frac{1}{\tau_i} & -\omega_i \\
			\omega_i & \frac{1}{\tau_i}
		\end{pmatrix}V_i(t)dt+\frac{2\nu_i}{\sqrt{\pi \tau_i}} dW(t) \\
		\log(\tau_i)=\log(\tau_{pre})+b_{\tau,pre}^{(i)} \\
	\log(\nu_i)=\log(\nu_{pre})+b_{\nu,pre}^{(i)}  \\
	\omega_i=\omega_{0,pre}+\sum_{k=1}^{L} \omega_{k,pre} \psi_k(E_{shore}^{(i)}(t_j^{(i)}),\Theta^{(i)}(t_j^{(i)})) + b_{\omega,pre}^{(i)}
	\end{array}
	\right.
\end{equation}

@@

	\end{array}
	\right.
	\label{eq: approximate baseline model}
\end{equation}
